Blocking-resistant communication\\through domain fronting

### 2015-02-11 docs/fronting.tex
Add Azure pricing to text.
Add in Lantern text.
Mostly unedited except for BibTeX cites.

% https://azure.microsoft.com/en-us/pricing/details/cdn/
\textbf{Microsoft Azure}~\cite{azure}
is a cloud computing platform that features a CDN.
Like CloudFront, Azure assigns automatically generated subdomains
of \urll{vo.msecnd.net}.
any of which can front for any other.
There are other possible front domain names, like \urll{ajax.aspnetcdn.com},
that are used as infrastructure by many web sites,
lending them high collateral damage.
Unlike CloudFront's, Azure's CDN works only for Azure-affiliated domains,
so as with App Engine, it is necessary to run a reflector app on Azure
that forwards requests to some other proxy proxy.

@@

Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.

Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

enproxy

automated scanner

>>>>

% https://azure.microsoft.com/en-us/pricing/details/cdn/
\textbf{Microsoft Azure}~\cite{azure}
is a cloud computing platform that features a CDN.
Like CloudFront, Azure assigns automatically generated subdomains
of \urll{vo.msecnd.net}.
any of which can front for any other.
There are other possible front domain names, like \urll{ajax.aspnetcdn.com},
that are used as infrastructure by many web sites,
lending them high collateral damage.
Unlike CloudFront's, Azure's CDN works only for Azure-affiliated domains,
so as with App Engine, it is necessary to run a reflector app on Azure
that forwards requests to some other proxy proxy.
Bandwidth is \$0.087--0.138/GB, with price breaks starting at 10~TB/month.

@@

Lantern~\cite{lantern} is a free circumvention tool targeting casual web browsing.
Lantern does not employ onion routing and in general does not provide the
same level of anonymity guarantees as Tor.  Lantern primarily focuses on
performance and availability.

At its core, Lantern is a network of shared HTTPS proxy servers combined
with a client application that allows censored users to find and use those
proxy servers to proxy traffic from their existing web browsers.  This same
client application also allows uncensored users to host such proxy servers
on their own networks for use by other Lantern users. Lantern ultimately
aims to provide a secure mechanism for distributing knowledge about both
Lantern-hosted and peer-hosted proxy servers using a trust-network based
distribution mechanism such as kaleidoscope~\cite{kaleidoscope}.  In the meantime, Lantern
also randomly assigns users to Lantern-hosted proxy servers.

Lantern uses a centralized infrastructure for authenticating users and
assigning proxies to them.  Lantern's threat model assumes that this
centralized infrastructure is or can be blocked by the censors.
Consequently, users must have a priori access to a functioning proxy which
they can use to bootstrap onto the Lantern network and learn about more
proxies. Prior to Lantern adopting domain-fronting, we gave users access to
such proxies (which we call fallbacks) by embedding their information in
customized software installers that we distributed directly to users.  This
prevented users from downloading Lantern directly and required them to
request an email invitation from us with a link to their custom installer.
Furthermore, since anyone could request an installer, the censors could
theoretically learn about all of our proxies simply by continually
requesting installers.

\subsection{Timeline for Deploying Domain-Fronting}

\begin{figure}
\centering
\includegraphics[height=1.5in]{lantern}
\caption{
Megabytes per second served by domain-fronted Lantern proxies
(Lantern-hosted and peers).
}
\label{fig:lantern-bandwidth}
\end{figure}

Lantern rolled out domain-fronting via CloudFlare in July 2014 in order to
allow users to direct-download Lantern without an email invitation.  In
this initial implementation, direct-downloaded Lantern clients proxied all
their traffic using domain-fronting.  It worked, and we experienced steady
growth in direct downloads and traffic from direct-downloaded clients.

At the beginning of October 2014, we started randomly assigning direct
HTTPS proxies to users who had direct-downloaded Lantern.  This diverted
traffic from domain-fronted servers to more efficient direct servers.

In December 2014 and January 2015, Lantern experienced a dramatic surge in
domain-fronted traffic, jumping from 1 MB/s to 100 MB/s within those two
months. At first we assumed that direct proxies had been blocked, but it
turns out that the majority of this new traffic originated in the
Philippines, which is not a heavily censored country. From what we're
hearing, it looks like Philippine users are using Lantern to get around
their ISPs bandwidth caps~\cite{needed}.

\subsection{General Deployment Considerations}

Unlike with meek, Lantern's equivalent of reflectors (which we call
proxies) are also exit nodes.  So in our infrastructure, we have:

user agent → Lantern client → CDN → Lantern proxy → destination.

Lantern hosts dozens of such proxies on commodity VPS providers like
Digital Ocean. In addition, uncensored users who run the Lantern client can
register themselves as domain-fronted proxies as well, so overall there are
theoretically a very large number of proxies in rotation at any one time.

\subsection{Choice of CDN}
In our initial implementation, we used Fastly as our CDN.  Fastly ended up
being unsuitable because their infrastructure isn't meant to support a
large number of backends, so we transitioned to CloudFlare.  CloudFlare has
worked well so far because it supports a large number of backends, it has
an API that we can use to manage those backends and it has cheap flat-rate
pricing that doesn't charge based on bandwidth consumption. It also has
a sufficient number of relatively high-profile domains through which we can
front.

\subsection{Implementation Components}
Lantern's domain fronting is implemented in Go and made available through
the flashlight~\cite{flashlight} application.
The core of flashlight's domain fronting is encapsulated in two libraries,
enproxy~\cite{enproxy} and fronted~\cite{fronted}.

enproxy provides an implementation of Go's standard net.Conn interface that
encapsulates reads and writes as a series of HTTP requests via a stateful
enproxy proxy.  This allows flashlight to proxy any streaming-oriented
traffic (e.g. TCP).  Unlike meek, enproxy supports full-duplex~\cite{beating-gfw-with-go} operation
so that reads don't wait on writes, which can be handy for bidirectional
protocols like XMPP.  Lantern actually uses XMPP as a signaling channel for
peer-to-peer traffic, and tunnels XMPP via domain-fronted proxies.

fronted uses domain-fronting to transmit enproxy's HTTP requests in a
blocking-resistant manner. It provides a facility for configuring a number
of different front domains (masquerade hosts) and includes the ability to
connect to them directly by IP address rather than DNS. In practice,
flashlight uses several hundred masquerade hosts when communicating via
CloudFlare.

\subsection{Sticky Routing}
Domain-fronted Lantern requests go to one of two host names,
fallbacks.getiantem.org and peers.getiantem.org.  Fallbacks is a pool of
servers hosted by Lantern, and peers is the pool of servers constituted by
online Lantern peers.  When using CloudFlare, a server is selected based by
round robin.  Just like with meek, Lantern's domain-fronting protocol is
stateful, so subsequent HTTP requests for the same connection need to find
their way back to the same proxy that handled the original request.  We
accomplish this by having the responding proxy return its specific hostname
in a header which the client then users on subsequent requests, thereby
bypassing the round robin.

\subsection{Added Latency in Domain-fronted Encapsulated HTTP Transports and
Mitigations for the Same}
Encapsulating a streaming network connection in a series of HTTP requests
introduces additional latency beyond TCP. In the case of flashlight and
CloudFlare, there are several causes of this latency:

Firstly, domain-fronting requires the establishment of additional TCP
connections. In a best case scenario, the user agent can open a single TCP
connection directly to the destination server.  With Lantern, the inclusion
of the client, CloudFlare and the proxy introduce three additional TCP
connections between the user agent and the destination.  This is mitigated
somewhat by the fact that CloudFlare pools and reuses connections to the
Lantern proxy.  Unfortunately, the Lantern client cannot do the same for
connections to CloudFlare as CloudFlare seems to time out idle connections
fairly aggressively.  We mitigate this somewhat by aggressively
pre-connecting to CloudFlare when we detect activity~\cite{connpool}.

Secondly, even though enproxy operates mostly in full-duplex, reads cannot
begin until the first request and the response containing the
sticky-routing header have been processed. There is no mitigation for this.

Thirdly, enproxy does not pipeline http requests.  This means that even
though reads and writes are full duplex, the flush of one set of writes
cannot proceed until the previous flush of the previous set of writes has
been acknowledged with an http response, meaning that a full round-trip is
necessary between each flush. Implementing HTTP 2.0 would provide request
pipelining and potentially improve on latency substantially.

Fourthly, enproxy has no way of knowing when the user agent is done
writing.  If the data were streaming directly from user agent through to
the proxy, this wouldn't be a problem, but CDNs like CloudFlare buffer
uploads fairly aggressively, so small uploads aren't actually forwarded to
the proxy until the HTTP request is finished.  enproxy assumes that a
writer is finished if it detects inactivity for more than 35 milliseconds,
at which point it flushes the write by finishing the HTTP request.  This
introduces at least 35 milliseconds of additional latency, and potentially
more if we guessed wrong and the write wasn't actually finished, since we
now have to wait for a full round trip before the next write can proceed.
This latency is particularly noticeable when proxying TLS traffic, as the
TLS handshake consists of several small messages sent back and forth
between user agent and server.

This fourth source of latency can be eliminated if enproxy can know for
sure when a writer is finished. This could be achieved by changing the
interface so that rather than implementing net.Conn and proxying generic
streams of traffic, enproxy could actually proxy HTTP requests directly. It
would be able to tell when the user agent is finished sending an HTTP
request and when the destination is finished responding.  However, doing
the same for HTTPS would require man-in-the-middling the TLS connection in
order to expose the flow of requests.  Furthermore, this approach only
works for HTTP clients.  Supporting other sorts of traffic like XMPP would
require implementing support for those protocols as well.

\subsection{Buffering versus Streaming Requests and Responses}
HTTP supports both buffered requests/responses (fixed content-length) and
streaming (chunked encoding). For large downloads and uploads in
particular, streaming is attractive because it allows writes to stream
through the proxy and CDN without blocking and as part of a single HTTP
request/response.  Some CDNs support streaming requests and responses, some
support only streaming responses, and some support neither streaming
requests nor responses.  CloudFlare supports streaming in both directions.

enproxy provides pluggable strategies to use either streaming or
buffering.

\subsection{Managing Proxy Rotations}
Lantern hosted proxies are fairly stable, but peer proxies tend to come
online and offline fairly frequently. The CDN (CloudFlare) configuration
needs to be kept up-to-date based on which proxies are available at any
given time. We achieve this using the peerscanner~\cite{peerscanner} application, which
provides a REST API for proxies to register and unregister themselves.
peerscanner does continual connectivity checking of registered proxies and
maintains the CloudFlare configuration accordingly. This process is
unfortunately not foolproof, because there is some latency in the
connectivity checking and some further latency in the updating of
CloudFlare's configuration and the propagation of those updates through
CloudFlare's infrastructure (haven't measured this).  This means that there
will be periods of time during which an offline proxy is still in rotation,
which causes an error for any user that's unlucky enough to get routed to
it.

\subsection{Direct Domain Fronting}
One of our services is a geolocation server. Rather than proxying traffic to it
via our enproxy proxies, we actually have it registered on CloudFlare and
domain-front to it directly.  This reduces latency and saves resources on our
end.  We've talked about doing direct domain-fronting for popular sites by just
registering their IPs in CloudFlare under special domains, for example
\urll{facebook.direct.getiantem.org}.  To do this for anything that's HTTPS would
require us to man-in-the-middle connections from the user agent.  The biggest
problem with man-in-the-middling isn't that our client-side Lantern software
sees the traffic in the clear, it's that the CDN also sees it in the clear.
